%% ----------------------------------------------------------------
%% Introduction.tex
%% ---------------------------------------------------------------- 


\chapter{Introduction} \label{Chapter:Introduction}
Darwin's Theory of Evolution states that variation of species in every generation leads to different probability of suvival and eventually those with the combination of characters which can adapt to environment has more opportunities to survive and their offspring will inherit these benefitual features. As time goes, this difference will enlarge and form a new population. From this point of view, it seems that every individual is independent and selfish. In real human society, however, phenomenon of spontaneous cooperation and defection exists, which is considered to be contrary to the principle of natural selection. In addition, as Thomas Hobbes says, social order should be established by powerful organisation. Thus, it is particularly confused how human being behave (cooperate or defect) in some specific situation. 

Research of migration patterns is one topic attracts increasing attention in this field. However, all the research is trying to model a specific scenario and simulate it to acquire results which means it lacks of a real application to study human's strategies in game theory or in particular, migration game. If an application can be built according to some rules and directly use it to investigate human's actual decisions in migration, it may be helpful to study cooperation in human society. This is the inspiration for the project.

This project focuses on creating web interface for people to play migration game based on Prisoner's Dilemma game. The overall procedure includes registering, filling a form of simple personal detail, playing the game and at the end, the data will be stored in the database for future analysis. In terms of saving information, it contains user data, position of players every time and strategy and payoff every round. This data is useful to figure out more about strategies when people migrate.

\section{Project Management}
Having a good plan and strictly following the schedule is helpful to have a successful accomplishment of the project. For my project, I divide into four stages:

\begin{enumerate}
\item It was of importance to do much background research before commencing. Therefore, related conceptions and recent research results should be comprehended by reading and basic ideas should be grasped. This was expected to spend  three weeks. Eventually, it spent three weeks and most time was spent to understand new concepts on game theory.
\item Based on the reading, design including user interface, business logic layer as well as data access layer should be respectively finished. Thinking of what the application would be was one of the most vital parts as a good design was the foundation of future development. During specific development, some detailed sections still could be modified. This was supposed to take two weeks. When this step carried out, it took a lot more time than expected, as long as four weeks because I misunderstood main models on migration and built a wrong fundamental web interface. Therefore, redesigning spent more time.
\item The third part of the project was to implement every functionality of the game. In this project, it could be estimated to use HTML, CSS and JavaScript to develop web interface and MySQL for data storage. It was speculated to use most time, as much as three to four weeks. Eventually, however, the second step consumed me much more time and the application even deviated from the correct game model at the beginning, which lead me to have to shorten time for developing. This stage finally took me three weeks.
\item Test to make sure it could run smoothly and acquire all the useful information in the database. If time permitted, the application should be tested by others to see if it was user-friendly and easy to administrate and maintain in the future. It aimed to provide information to people who wanted to find out what strategies individuals would have on migration, so strong information for analysis was one of essential testings.
\end{enumerate}

\section{Contribution}
Much related knowledge about prisoner's dilemma was learnt and some models of evolutionary migration game were more familiar which made me have a better understanding of game theory. Additionally, existing skills were developed. Programming in JavaScript associating with PHP and MySQL was practiced and it was definitely beneficial to my future development. Other abilities such as HTML and CSS played a significant role in the project and mixed using of programming languages made me know deeply about their various functions when creating an interactive and effective application.
